The Effects of the NBA COVID Bubble on the NBA Playoffs: A Case Study for Home-Court Advantage

### 2022-02-08 Manuscript/manuscript.tex
Update manuscript.tex
Changing float to tbp, and width control out of tex since 3/4 aspect ratio is in R

\jy{use `tbp' for figure/table locations instead of `H', unless it is
  required by the journal}

\jy{remake the figure~\ref{fig:Fig1}: make aspect 3:4 (height:width;
  increase the font size of the annonations; control the height/weight
  from within R now that we know how the figures will appear in the
  published version (so that you don't need to control width in latex.}

\jy{explain what the vertical lines are in all the figure captions}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=0.4\linewidth]{Fig1}
  \caption{Winning percentage of NBA home teams in the playoffs since
    2010, the green line denotes .500.}
  \label{fig:Fig1}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.4\linewidth]{Fig2}
  \caption{Histograms of home (blue) and away (red) scoring
    for 2020 (bottom) and 2017-2019 (top).}
  \label{fig:Fig2}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.4\linewidth]{Fig3}
  \caption{Histograms of home shooting percentages for two-
    pointers, three-pointers and free throws for 2020 (top) vs.~2017--19
    (bottom).}
  \label{fig:Fig3}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.4\linewidth]{Fig4}
  \caption{Histograms of away shooting percentages for two-pointers,
    three-pointers and free throws for 2020 (top) vs.~2017--19
    (bottom).}
  \label{fig:Fig4}  
\end{figure}

>>>>

\begin{figure}[tbp]
  \centering
  \includegraphics{Fig1}
  \caption{Winning percentage of NBA home teams in the playoffs since
    2010, the green line denotes .500.}
  \label{fig:Fig1}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics{Fig2}
  \caption{Histograms of home (blue) and away (red) scoring
    for 2020 (bottom) and 2017-2019 (top).}
  \label{fig:Fig2}
\end{figure}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics{Fig3}
  \caption{Histograms of home shooting percentages for two-
    pointers, three-pointers and free throws for 2020 (top) vs.~2017--19
    (bottom).}
  \label{fig:Fig3}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics{Fig4}
  \caption{Histograms of away shooting percentages for two-pointers,
    three-pointers and free throws for 2020 (top) vs.~2017--19
    (bottom).}
  \label{fig:Fig4}  
\end{figure}
